---
title: Alien plants are associated with decrease in local and regional native richness even at low abundances
author: "Maud Bernard-Verdier"
date: 
output: 
  html_document: 
    toc: yes
---

Last updated: `r date()`

```{r setup, echo=FALSE, warning=FALSE}
require(knitr)

if( length(grep('mac', .Platform$pkgType) ) == 0){
knitr::opts_knit$set( root.dir = "/Users/maud/Dropbox/Work/doc boulot/postdoc Lincoln/R_alienimpactBP")
}

print(getwd())
knitr::opts_chunk$set( echo = FALSE, warning=FALSE)

# packages
library(doBy)

```

```{r loaddata, echo=FALSE, warning=FALSE}

# load data and results
load("/Users/maud/Dropbox/Work/doc boulot/postdoc Lincoln/R_alienimpactBP/saved Rdata/article 2 - threshold/article threshold 1.3.1.Rdata")

#default graphical parameters
.defaultpar <- par(no.readonly = T)

# Defining variables 
abclasses= c("Rare" ,"Occasional",  "Frequent", "Common", "Abundant","Dominant")
threshold ="th.CI"
sel <- impsp

# loss in gamma native richness
dg<- table.div.part$deltagamma - table.div.part$delta.null.permute.all
dg1<- table.div.part$deltagamma - table.div.part$delta.null.beta
dg2<- table.div.part$GRc - table.div.part$GRnull

# loss in alpha native richness
da<- table.div.part$aRc -  table.div.part$aRo
da1<- table.div.part$aRc -  table.div.part$aRnull

#spatial distributions:
spread <- table.div.part$n.plot.impact
prevalence <- table.div.part$prevalence

```
## Numerical results

The total species pool is `r (tot <-sum(colSums(comm[unimprovedgrasslands,])>0))` species, of which `r (tot.ali <- sum(colSums(comm[unimprovedgrasslands,names(comm) %in% aliens])>0))` (`r  round(tot.ali/tot *100,0)`%) are aliens and 
`r (tot.nat <- sum(colSums(comm[unimprovedgrasslands,names(comm) %in% natives])>0))`
are natives.

We study `r length(rownames(glmSRnat.overall$dif))` focal species, including `r sum(rownames(glmSRnat.overall$dif) %in% aliens)` aliens (
`r round(sum(rownames(glmSRnat.overall$dif) %in% aliens)/length(rownames(glmSRnat.overall$dif))*100, 0)`
%).

```{r echo=FALSE}
tbl <- matrix(c(sum(rownames(glmSRnat.overall$dif) %in% natives), tot.nat,sum(rownames(glmSRnat.overall$dif) %in% aliens), tot.ali), nrow=2, ncol=2)
f<- fisher.test(tbl) 
```

This is a non random subsample of the total pool of species in terms of alien status (Fisher exact test: odds ratio = `r round(f$estimate,2)`, P = `r round( f$p.value, 3)` )


```{r echo=FALSE}
# Stats
tbl <- glmSRnat.sum$overall.summary
tbl$nothr <- tbl$nb.sp - tbl$freq.thr
tbl= t(tbl[,3:4])
f<- fisher.test(tbl)  #### the only interesting one -> not signif if more stringent on robustness...
```

We found negative critical abundances for `r glmSRnat.sum$overall.summary[2,3]` aliens and `r glmSRnat.sum$overall.summary[1,3]` native. This corresponds to a  higher proportion of aliens vs. natives given the focal species pool (Fisher exact test: odds ratio = `r round(f$estimate,2)`, P = `r round(f$p.value, 3)` )
 

Above critical abundances, we lose on average 
 `r round(mean(da),2)` (+- `r round(sd(da),2)`) species in mean alpha richness, and 
 `r round(mean(dg),2)` (+- `r round(sd(dg),2)`) species in total gamma richness compared to the null model accounting for sample size.


## Table 1

```{r}
print(table.div.part[, c("th.CI", "prevalence", "n.plot.impact","aRo", "aRc", "GRo", "GRc", "GRP.permute.all","GRP.beta")])
```

# Figures paper:
## Figure 1: barplot of frequencies:  
```{r frequency.p, echo=FALSE}

effects =glmSRnat.sum$class.summary

n <- length(unique(effects$group)) 

par(mfcol=c(1,2), oma=c(2,2,3,1), mar=c(2,2,1,2), las=1)

sum.df = effects
  for (i in 1:n) {
  S <- as.data.frame(sum.df[sum.df$group == unique(sum.df$group)[i],])
  barplot(S$nb.sp, ylim=c(0,max(40, S$nb.sp)),col= "grey",  border= NA, axes=F)

  par(new=T)
  barplot(S$freq.negative.above, ylim=c(0,max(40, S$nb.sp)),col= "grey50",  border= NA, axes=F)

  par(new=T)
  b <- barplot(S$freq.thr, col="black" , ylim=c(0,max(40, S$nb.sp)), border= NA, axes=F)
  
  axis(2, tcl = -0.3, cex.axis = 0.8, mgp = c(1,0.5,0), las = 1)
text(y=-3, x = b, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
    
if ( i==1) {
legend(x=1, y=40, bty="n", bg="white",legend=c("Critical abundance","Negative trend", "Total observed"), fill=c("black","grey50",  "grey"), border= c("black", "grey50", "grey"), cex=0.9, xpd=NA)
    }
  }   
mtext(text="number of species", side=2, outer=T, line=0, las=0, cex=0.85) 

mtext(side=3, text=c("a) Native focal species","b) Alien focal species"),line=0, at=c(0.05,0.55),adj=0, outer=T, las=1)

mtext(text="Abundance class", side=1, outer=T, line=3)

```

## Figure 1bis: barplot of negative vs. positive proportions:  
```{r prop.neg, echo=FALSE}

effects =list(glmSRnat.sum$class.summary,glmSRali.sum$class.summary )     

n <- length(unique(effects[[1]]$group)) 

par(mfcol=c(n,2), oma=c(5,6,4,1), mar=c(1,1,1,2), las=1)
for (j in 1:2) {
  sum.df = effects[[j]] 
  for (i in 1:n) {
  S <- as.data.frame(sum.df[sum.df$group == unique(sum.df$group)[i],])
 b <-  barplot(rep(1,5), ylim=c(0,1),col= "white",  border= "grey", axes=F)

  par(new=T)
   barplot(S$freq.positive.sig/S$nb.sp + S$prop.negative.sig, ylim=c(0,1), col= "grey60",  border= NA, axes=F)
     par(new=T)
  barplot(S$prop.negative.sig, ylim=c(0,1),col= "grey30",  border= NA, axes=F)


  axis(2, tcl = -0.3, cex.axis = 0.8, mgp = c(1,0.5,0), las = 1)
  if (i==2) text(y=-3, x = b, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
    
  # Add spearman test
  fit <- cor.test(1:5,as.numeric(S$prop.negative.sig), method = "spearman", exact = FALSE) 
  mtext(3, text=paste(round(fit$estimate,2), p2star(fit$p.value)) ,
        font = 1, outer= F,adj=0.99, cex=0.7, line=0, las = 1)

  
    if (j==2 & i==2) {
      legend("topright", bty="o", box.col = "white", bg="white",legend=c("Positive ES", "Negative ES"),fill=c("grey60",  "grey30"), cex=0.9, xpd=NA)
    }
    if(j==1) {
      mtext(text="number of species", side=2, outer=F, line=1.5, las=0, cex=0.85) 
    }
  }   
}

mtext(side=2, text=c("Alien\nfocal\nspecies", "Native\nfocal\nspecies"),line=4, at=c(0.25,0.75),adj=0.5, outer=T, las=1)
mtext(side=3, text=c("a) Native richness", "b) Alien richness"),line=0, at=c(0.25,0.75),adj=0.5, outer=T, las=1)

mtext(text="Abundance class", side=1, outer=T, line=3)
```

## Figure 2: trends in alpha effect size for `r length(sel)` species:
```{r ARalphatrends, echo = FALSE}

par(mfrow = c(3,4), mar=c(2,0,1,2), oma=c(5,6,1,1))
sel <- impsp
M <- glmSRnat.overall
  ylim=c(-3,3)
  ### Loop on selected species 
  for (i in 1:length(sel))  {
    # if (i ==4) plot.new()
    sp <- sel[i]
    es <- as.numeric(M$est[sp,])
    n <- as.numeric(M$n.obs[sp,])[2:6]
    
      low <- as.numeric(M$CIlow[sp,])
      hi <- as.numeric(M$CIhi[sp,])
      M$thresh <-M$impact.spread
        ## correct for small sample sizes
    small <- es
    small[which(n>=5)] <- NA
    es[which(n<5)] <- NA
    low[n<5] <- NA
    hi[n<5] <- NA
    
    if ( !all(is.na(c(hi, low)))) lims <-  max(c(abs(low),abs(hi)), na.rm=T) +0.02
    if ( all(is.na(c(hi, low)))) lims <-  max(c(abs(es)), na.rm=T) +0.02

    col <- rep("white",6)
    col[(1:6)>= as.numeric( M$thresh[sp,threshold])] <- "black"  # above threshold
    col[(2:6)[hi>0]] <- NA  # robust negative coef
    col[(2:6)[n<5]] <- NA  # sufficient data points
    # 
    # ylim=c(-max(lims,2 ), +max(lims,2))
      
    plot(1:5,  rep(0,5),ylim=ylim, xlim = c(0.5, 5.5), type= "n", xaxt = "n", yaxt="n", ann=F)

    axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
    if (i %in% c(9:12)) text(y=-3.6, x = 1:5, labels= abclasses[2:6],  cex=1, srt=45, adj=1, xpd = NA)
    
    if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
    abline(h=0,lty="dotted")
    abline(v = M$thresh[sp,threshold]-1, lty="dashed")
    
    if (!all(is.na(small))) points(1:5, small, pch=".")  
    
    ## Add bootstrapped CI
    if ( !all(is.na(c(hi, low)))) {
      arrows(1:5,low,   1:5,hi, lwd=1, code =3, length=0.05, angle=90)
    }
    
#     fit <- cor.test(1:5, es, method = "spearman")
#     mtext(3, text = substitute(italic(rho) *' = '*a*b, list(a=eval(round(fit$est, 2)), b= p2star(fit$p.value))), cex = 0.5, adj = 1, line = -1)
 
    # draw the points and lines
    par(new=T)
    plot(1:5,es, bg = col[2:6], pch=21, type = "p",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
    
    # Add species name
     if( sp %in% aliens) {mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)}
     if( sp %in% natives) {mtext(3, text=paste("*", species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)}
    
    
    # Y axis label
    if ( i %in% c(1,5,9)) {  
    mtext(2, text="GLM coefficient",adj=0.5, cex=0.7, line=1.5, las = 0)
    }
   }

mtext(1, text=c("Abundance class"), adj=0.5, line=3, las = 1, outer=T)
mtext(2, text=c("Effect on native alpha richness"), adj=0.5, line=4, las = 0, outer=T)

```

## Figure 2bis: trends in ALIEN alpha effect size for `r length(sel)` species:
```{r alphatrends, echo = FALSE}

par(mfrow = c(3,4), mar=c(0,0,2,2), oma=c(6,6,2,3))
sel <- impsp
M <- glmSRali.overall
  ylim=c(-1,1)
  ### Loop on selected species 
  for (i in 1:length(sel))  {
    # if (i ==4) plot.new()
    sp <- sel[i]
    es <- as.numeric(M$est[sp,])
    n <- as.numeric(M$n.obs[sp,])[2:6]
    
      low <- as.numeric(M$CIlow[sp,])
      hi <- as.numeric(M$CIhi[sp,])
      M$thresh <-M$impact.spread
    
    ## correct for small sample sizes
    small <- es
    small[which(n>=5)] <- NA
    es[which(n<5)] <- NA
    low[n<5] <- NA
    hi[n<5] <- NA
    
    if ( !all(is.na(c(hi, low)))) lims <-  max(c(abs(low),abs(hi)), na.rm=T) +0.02
    if ( all(is.na(c(hi, low)))) lims <-  max(c(abs(es)), na.rm=T) +0.02

    col <- rep("white",6)
    col[(1:6)>= as.numeric( M$thresh[sp,threshold])] <- "black"  # above threshold
    col[(2:6)[hi>0]] <- NA  # robust negative coef
    col[(2:6)[n<5]] <- NA  # sufficient data points
    
    
    plot(1:5,  rep(0,5),ylim=ylim, xlim = c(0.5, 5.5), type= "n", xaxt = "n", yaxt="n", ann=F)

    axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
    if (i %in% c(9:12)) text(y=-1.6, x = 1:5, labels= abclasses[2:6],  cex=0.9, srt=45, adj=1, xpd = NA)
    
    if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
    abline(h=0,lty="dotted")
    abline(v = M$thresh[sp,threshold]-1, lty="dashed")
    
    if (!all(is.na(small))) points(1:5, small, pch=".")  
    
    ## Add bootstrapped CI
    if ( !all(is.na(c(hi, low)))) {
      arrows(1:5,low,   1:5,hi, lwd=1, code =3, length=0.05, angle=90)
    }
    
    # draw the points and lines
    par(new=T)
    plot(1:5,es, bg = col[2:6], pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
    
    # Add species name
     mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)
    
    
    # Y axis label
    if ( i %in% c(1,5,9)) {  
    mtext(2, text="GLM coefficient",adj=0.5, cex=0.7, line=1.5, las = 0)
    }
   }

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect on alien alpha richness"), adj=0.5, line=4, las = 0, outer=T)

```

## Figure 3: trends in gamma effect size for `r length(sel)` species:
```{r gammatrends, echo=FALSE}

par(mfrow = c(3,4), mar=c(2,0,1,2), oma=c(5,6,1,1))
ylim = c(-50,35)
xlim = c(0.5, 5.5)

for (i in 1 : length(impsp)){
  
  # if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (gamma.trend.nat$P.gamma[sp,] <=0.025) +1]
  n <- as.numeric(glmSRnat.overall$n.obs[sp,])[1:6]
  # create x axis for the 5 abundance classes
  x = c(0:5)

  # create y axis with the gamma richness Standardized effect size
  y = (gamma.trend.nat$obs[sp,] - gamma.trend.nat$mean.null[sp,])
  y [ (1:6)[ n < 5] ]=NA
  y[1]=NA

    # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)

  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(9:12)) text(y=-60, x = 1:5, labels= abclasses[2:6],  cex=1, srt=45, adj=1, xpd = NA)

  axis(2, tcl= 0.1, label=F,  mgp=c(1,0.5,0), las=1)
  if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)
  abline(h=0,lty="dotted")
  abline(v =glmSRnat.overall$impact.spread[sp,threshold]-1, lty="dashed")


  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)

   # Add species name
     if( sp %in% aliens) {mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)}
     if( sp %in% natives) {mtext(3, text=paste("*", species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)}
    
  
#   # Add spearman test
#   fit <- cor.test(1:6,as.numeric(y), method = "spearman", exact = FALSE) 
#   mtext(1, text=paste(round(fit$estimate,2), p2star(fit$p.value)) ,
#         font = 1, outer= F,adj=0.99, cex=0.7, line=-1, las = 1)

  # Y axis label
  if ( i %in%  c(1,5,9)){
    mtext(2, text="ES",adj=0.5, cex=0.8, line=1.5, las = 0)
  }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=3, las = 1, outer=T)
mtext(2, text=c("Effect on Native gamma richness"), adj=0.5, line=4, las = 0, outer=T)


```


## Figure 4: Graphs of delta gamma vs. delta gamma:

```{r deltagamma.deltaalpha, echo = FALSE}

par(mfrow = c(1,1), mar=c(4,3,2,1), oma=c(0,0,0,0), las = 1)
cgam <- c("grey50", "black")[ (table.div.part$GRP.permute.all<=0.05) + 1]
plot(da, dg ,pch = 20, col=cgam , ann=F, xlim= c(-4,0), type ="n",mgp=c(0,0.5,0), tcl=-0.2 ,cex.axis = 0.9)

text(x = da,y = dg,label = rownames(table.div.part) , col=cgam, cex =0.7)

f <- cor.test(da ,dg)
mtext(3, text = substitute(italic(r == est *" "*p), list(est = round(f$est,2), p=p2star(f$p.val, marginal=F))),adj = 1, cex=0.8, font = 3)

mtext(1,text = expression(Delta*alpha), line=2 )
mtext(2,text = expression(Delta*gamma["c"]), line=2  , las=0)

```


## Figure 5: Graphs of delta gamma vs. spread:

```{r deltagamma.spread, echo = FALSE}

par(mfrow = c(1,1), mar=c(4,3,2,1), oma=c(0,0,0,0), las = 1)
print(f <- cor.test(spread ,dg))

plot (spread,dg , pch = 20, col=cgam , ann=F, log = "x", xlim =c(2.5, 700),  type ="n",mgp=c(0,0.5,0), tcl=-0.2 ,cex.axis = 0.9)

text(x = spread, y = dg,label = rownames(table.div.part),col=cgam, cex=0.7)

mtext(3, text = substitute(italic(r == est *" "*p), list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),adj = 1, cex=0.8)

mtext(1,text = "Number of plots > critical abundance", line=2 )
mtext(2,text = expression(Delta*gamma["c"]), line=2  , las=0)


```

## Figure 6: Graphs of delta alpha  vs. prevalence:

```{r deltagamma.prevalence, echo = FALSE}
par(mfrow = c(2,1), mar=c(3,2,2,1), oma=c(1,2,0,0), las = 1)

# loss in alpha 
print(f <- cor.test(prevalence,da))

plot (prevalence,da , pch = 20, col=cgam , ann=F, log = "x", xlim =c(100, 900), type= "n")
text(x = prevalence, y = da,label = rownames(table.div.part), cex=0.7)

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Number of plots", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" alpha richness"), line=2.5  , las=0, cex =0.85)


# loss in gamma
print(f <- cor.test(prevalence,dg))

plot (prevalence,dg , pch = 20, col=cgam , ann=F, log = "x", xlim =c(100, 900), type= "n")
text(x = prevalence, y = dg,label = rownames(table.div.part), cex=0.7)

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Number of plots", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)

```


# some alternative figures : 


## Loss in alpha richness vs. critical abundance

Mean loss in alpha richness is not correlated to the critical abundance value, although 

```{r deltaalpha.vs.crit, echo =FALSE}
thr <-  glmSRnat.overall$impact.spread[impsp,  "th.CI"]

plot (thr,da, pch = 20, col=cgam , ann=F,  type="n")
f <- cor.test(da,thr)

text(x = thr,
     y = da, label = impsp ,col="black", cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "critical abundance", line=2.5, cex =0.85 )
mtext(2,text ="alpha loss", line=2.5  , las=0, cex =0.85)

print(f)
```
### Loss in gamma richness vs. spatial proportion of potential impact

```{r deltagam.impactproportion, echo =FALSE}
par(mfrow = c(1,1), mar=c(4,4,2,1), oma = c(1,1,1,1))
spread <-  glmSRnat.overall$impact.spread[impsp,  "prop.plot.impact"]
plot (spread,dg , pch = 20, col=cgam , ann=F, xlim =c(0, 1), type="n")
f <- cor.test(spread ,dg)

text(x = spread,
     y = dg,
     label = rownames(table.div.part) ,col="black", cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "Prop. of plots > critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
```



## Trends in gamma above vs.below trends
```{r gamma.above-below, echo = FALSE}
par(mfrow = c(3,4), mar=c(0,0,1,1), oma=c(6,6,2,1))

list.data <-gamma.above.nat.permute.all
gamma.loss <- as.data.frame(matrix(NA, nrow = length(impsp), ncol =6))
rownames(gamma.loss) <- impsp

ylim=c(-70,70)
for (i in 1 : length(impsp)){
  
  # if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (list.data$P.above[sp,] <=0.025) +1]
  n <- list.data$nplot.above[sp,]
  # create x axis for the 5 abundance classes
  x = c(0:5)
  
  # create y axis with the gamma richness Standardized effect size
  y =  (list.data$gamma.above[sp,] - list.data$null.above[sp,])/ list.data$null.above[sp,]
  
    y =  -(list.data$null.delta[sp,] - list.data$deltagamma[sp,])
    
  y [ (1:6)[ n < 5 | is.na(n)] ]=NA
  y[1]=NA
  
  gamma.loss[sp,] = y
  
  # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)
  
  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(9,10,11,12)) text(y=-72.5, x = 1:5, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
  
  if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
  abline(h=0,lty="dotted")
  
  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
  
  # Add species name
  mtext(3, text=paste(species[sp, "Genus"], "\n",species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=-2.5, las = 1)
  
  #   # Y axis label
  #   if ( i %in% c(1,4,7)) {  
  #     mtext(2, text="SES", ,adj=0.5, cex=0.8, line=1.5, las = 0)
  #   }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect size of native gamma richness"), adj=0.5, line=3, las = 0, outer=T)
```




## Change in gamma frequency above/below critical threshold on native richness 
```{r}
par(mfrow=c(3,4), mar=c(2,2,2,2), oma= c(2,3,1,1))
for (sp in impsp) {

  community <- comm[which((rownames(comm) %in% realgrasslands) & (comm[,sp]>0) ),-grep(sp, names(comm))]
  community <- ceiling(community>0)
  community <- community[,colSums(community)>0]

  comm.nat<- community[,colnames(community) %in% natives]
  comm.ali<- community[,colnames(community) %in% aliens]

  var <- comm[rownames(community),sp]
  var[var < glmSRnat.overall$impact.spread [sp,"th.CI"]] <- 0
  var[var >= glmSRnat.overall$impact.spread [sp,"th.CI"]] <- 1

  B.freq <- colSums(comm.nat[var==0,])/sum(var==0)
  A.freq <- colSums(comm.nat[var==1,])/sum(var==1)
  B.freq.ali <- colSums(comm.ali[var==0,])/sum(var==0)
  A.freq.ali <- colSums(comm.ali[var==1,])/sum(var==1)

  cvec <-  c("black","red")[(A.freq == 0) + 1]
  sum((A.freq == 0) )
  cvec [B.freq == 0] <- "forestgreen"
  sum(B.freq == 0)

  f1 <- wilcox.test(  A.freq ,B.freq, paired=T, alternative = "less")
  c1 <- cor.test( A.freq , B.freq, method = "spearman")

  #correlation plot
#   plot(jitter(B.freq, factor = 1), jitter(A.freq, factor=1),
#        ylim=c(-0.01,0.9), xlim=c(-0.01,0.9),pch=21, bg =cvec,
#        ann=F, axes =F)
  plot(B.freq+0.005, A.freq+0.005,log="xy",type = "n", pch=21, bg =cvec, ann=F, axes =F,
       ylim=c(0.005, 0.9), xlim=c(0.005,0.9))

  abline(0,1)
  mtext(paste(sp, "\n rho=", round(c1$est, 2), p2star(c1$p.val)), cex = 0.7)

  points(B.freq.ali+0.005, A.freq.ali+0.005,log="xy",pch=3, cex=0.85, col="grey")
  points(B.freq+0.005, A.freq+0.005, pch=21, bg =cvec)

#   axis(1, at =c(0.005,0.01,seq(0.1,0.9,0.1)),label=c(0,0.01,seq(10,90,10)), tcl = 0.2,mgp=c(1,0.2,0), cex=0.7)
#   axis(2, at =c(0.005,0.01,seq(0.1,0.9,0.1)),label=c(0,0.01,seq(10,90,10)), tcl = 0.2,mgp=c(1,0.2,0),las=1,  cex=0.7)
  axis(1, tcl = 0.2,mgp=c(1,0.2,0), cex=0.7)
 axis(2,tcl = 0.2,mgp=c(1,0.2,0),las=1,  cex=0.7)

  box(bty="l")
}
mtext(side = 1, text =c("below critical"),cex = 1, line=0,outer= T)
mtext(side = 2, text =c("above critical"),cex = 1, line= 1,outer= T)
```


## Figure 4bis: Graphs of delta gamma vs. delta gamma(2):

```{r deltagamma2.deltaalpha, echo = FALSE}

par(mfrow = c(1,1), mar=c(4,3,2,1), oma=c(0,0,0,0), las = 1)
cgam <- c("grey50", "black")[ (table.div.part$GRP.beta<=0.05) + 1]
plot(da, dg1 ,pch = 20, col=cgam , ann=F, xlim= c(-4,0), type ="n",mgp=c(0,0.5,0), tcl=-0.2 ,cex.axis = 0.9)

text(x = da,y = dg1,label = rownames(table.div.part) , col=cgam, cex =0.7)

f <- cor.test(da ,dg1)
mtext(3, text = substitute(italic(r == est *" "*p), list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),adj = 1, cex=0.8, font = 3)

mtext(1,text = expression(Delta*alpha), line=2 )
mtext(2,text = expression(Delta*gamma["c"]), line=2  , las=0)

```


## Figure 5: Graphs of delta gamma vs. spread:

```{r deltagamma2.spread, echo = FALSE}

par(mfrow = c(1,1), mar=c(4,3,2,1), oma=c(0,0,0,0), las = 1)
print(f <- cor.test(spread ,dg1))

plot (spread,dg1 , pch = 20, col=cgam , ann=F, log = "x", xlim =c(2.5, 700),  type ="n",mgp=c(0,0.5,0), tcl=-0.2 ,cex.axis = 0.9)

text(x = spread, y = dg1,label = rownames(table.div.part),col=cgam, cex=0.7)

mtext(3, text = substitute(italic(r == est *" "*p), list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),adj = 1, cex=0.8)

mtext(1,text = "Number of plots > critical abundance", line=2 )
mtext(2,text = expression(Delta*gamma["c"]), line=2  , las=0)


