---
title: Alien plants are associated with decrease in local and regional native richness
  even at low abundances
author: "maudbv"
date: "6 August 2015"
output: html_document
---


```{r setup, echo = FALSE, warning=FALSE}
require(knitr)
if( length(grep('mac', .Platform$pkgType) ) == 0){
knitr::opts_knit$set( root.dir = "C:/Users/bernarm2/Dropbox/Work/doc boulot/post doc Lincoln/R_alienimpactBP")
}

 if( length(grep('mac', .Platform$pkgType) ) == 1) {
knitr::opts_knit$set( root.dir = "~/Dropbox/Work/doc boulot/post doc Lincoln/R_alienimpactBP")
 }

knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
# packages
library(doBy)

```

```{r loaddata, echo = FALSE, warning=FALSE}

# load data and results
load("saved Rdata/article 2 - threshold/article threshold 1.3.Rdata")

#default grpahical parameters
.defaultpar <- par(no.readonly = T)

# Define some elements
abclasses= c("Rare" ,"Occasional",  "Frequent", "Common", "Abundant","Dominant")
threshold ="th.CI"
sel <- impsp
```
## Numerical results

We focus on `r length(unique( as.character(db$PlotName)))` plots of unimproved grasslands.
We study `r length(rownames(glmSRnat.overall$dif))` focal species (`r sum(rownames(glmSRnat.overall$dif)%in% aliens)` aliens), among a total of `r length(unique(db$SpeciesCode))` vascular plant species (`r sum(unique(db$SpeciesCode)%in% aliens)` aliens). 


## Table 1

```{r}
print(table.div.part)
```

Above critical abundances, we lose on average compared to below : 
 `r round(mean(out$aRo - out$aRc),2)` (+- `r round(sd(out$aRo - out$aRc),2)`) species in mean alpha richness

 Above critical abundances, we lose on average compared to the null model : 
 `r round(mean(out$alpha.loss),2)` (+- `r round(sd(out$alpha.loss),2)`) species in mean alpha richness
 `r round(mean(out$gamma.loss),2)` (+- `r round(sd(out$gamma.loss),2)`) species in total gamma richness

### Figure 1: barplot of frequencies:  
```{r frequency, echo=FALSE}

effects =list(glmSRnat.sum$class.summary,glmSRali.sum$class.summary )     

n <- length(unique(effects[[1]]$group)) 

par(mfcol=c(n,2), oma=c(5,6,4,1), mar=c(1,1,1,2), las=1)
for (j in 1:2) {
  sum.df = effects[[j]] 
  for (i in 1:n) {
  S <- as.data.frame(sum.df[sum.df$group == unique(sum.df$group)[i],])
  barplot(S$nb.sp, ylim=c(0,max(40, S$nb.sp)),col= "grey",  border= NA, axes=F)

  par(new=T)
  barplot(S$freq.negative.above, ylim=c(0,max(40, S$nb.sp)),col= "grey50",  border= NA, axes=F)

  par(new=T)
  b <- barplot(S$freq.thr, col="black" , ylim=c(0,max(40, S$nb.sp)), border= NA, axes=F)
  
  axis(2, tcl = -0.3, cex.axis = 0.8, mgp = c(1,0.5,0), las = 1)
     if (i==2) text(y=-3, x = b, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
    
    if (j==2 & i==1) {
      legend(x=0.3, y=40, bty="n", bg="white",legend=c("Critical abundance", "Total occurrences"),
             fill=c("black",  "grey"), border= c("black",  "grey"), cex=0.9, xpd=NA)
    }
    if(j==1) {
      mtext(text="number of species", side=2, outer=F, line=1.5, las=0, cex=0.85) 
    }
  }   
}

mtext(side=2, text=c("Alien\nfocal\nspecies", "Native\nfocal\nspecies"),line=4, at=c(0.25,0.75),adj=0.5, outer=T, las=1)
mtext(side=3, text=c("a) Native richness", "b) Alien richness"),line=0, at=c(0.25,0.75),adj=0.5, outer=T, las=1)

mtext(text="Abundance class", side=1, outer=T, line=3)
```
  
### Figure 2: trends in alpha effect size for `r length(impsp)` species:
```{r NRalphatrendsES, echo = FALSE}

par(mfrow = c(4,4), mar=c(0,0,2,2), oma=c(6,6,2,3))
sel <- impsp
M <- glmSRnat.overall
  ylim=c(-3,3)
  ### Loop on selected species 
  for (i in 1:length(sel))  {
    # if (i ==4) plot.new()
    sp <- sel[i]
    es <- as.numeric(M$est[sp,])
    n <- as.numeric(M$n.obs[sp,])[2:6]
    
      low <- as.numeric(M$CIlow[sp,])
      hi <- as.numeric(M$CIhi[sp,])
      M$thresh <-M$impact.spread
    
    ## correct for small sample sizes
    small <- es
    small[which(n>=3)] <- NA
    es[which(n<3)] <- NA
    low[n<3] <- NA
    hi[n<3] <- NA
    
    if ( !all(is.na(c(hi, low)))) lims <-  max(c(abs(low),abs(hi)), na.rm=T) +0.02
    if ( all(is.na(c(hi, low)))) lims <-  max(c(abs(es)), na.rm=T) +0.02

    col <- rep("white",6)
    col[(1:6)>= as.numeric( M$thresh[sp,threshold])] <- "black"  # above threshold
    col[(2:6)[hi>0]] <- NA  # robust negative coef
    col[(2:6)[n<5]] <- NA  # sufficient data points
    
    
    plot(1:5,  rep(0,5),ylim=ylim, xlim = c(0.5, 5.5), type= "n", xaxt = "n", yaxt="n", ann=F)

    axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
    if (i %in% c(10:13)) text(y=-3.6, x = 1:5, labels= abclasses[2:6],  cex=0.9, srt=45, adj=1, xpd = NA)
    
    if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
    abline(h=0,lty="dotted")
    abline(v = M$thresh[sp,threshold]-1, lty="dashed")
    
    if (!all(is.na(small))) points(1:5, small, pch=".")  
    
    ## Add bootstrapped CI
    if ( !all(is.na(c(hi, low)))) {
      arrows(1:5,low,   1:5,hi, lwd=1, code =3, length=0.05, angle=90)
    }
    
    # draw the points and lines
    par(new=T)
    plot(1:5,es, bg = col[2:6], pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
    
    # Add species name
     mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)
    
    
    # Y axis label
    if ( i %in% c(1,5,9,13)) {  
    mtext(2, text="GLM coefficient",adj=0.5, cex=0.7, line=1.5, las = 0)
    }
   }

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect on native alpha richness"), adj=0.5, line=4, las = 0, outer=T)

```

### Figure 2: trends in ALIEN alpha effect size for `r length(impsp)` species:
```{r ARalphatrendsES, echo = FALSE}

par(mfrow = c(4,4), mar=c(0,0,2,2), oma=c(6,6,2,3))
sel <- impsp
M <- glmSRali.overall
  ylim=c(-1,1)
  ### Loop on selected species 
  for (i in 1:length(sel))  {
    # if (i ==4) plot.new()
    sp <- sel[i]
    es <- as.numeric(M$est[sp,])
    n <- as.numeric(M$n.obs[sp,])[2:6]
    
      low <- as.numeric(M$CIlow[sp,])
      hi <- as.numeric(M$CIhi[sp,])
      M$thresh <-M$impact.spread
    
    ## correct for small sample sizes
    small <- es
    small[which(n>=3)] <- NA
    es[which(n<3)] <- NA
    low[n<3] <- NA
    hi[n<3] <- NA
    
    if ( !all(is.na(c(hi, low)))) lims <-  max(c(abs(low),abs(hi)), na.rm=T) +0.02
    if ( all(is.na(c(hi, low)))) lims <-  max(c(abs(es)), na.rm=T) +0.02

    col <- rep("white",6)
    col[(1:6)>= as.numeric( M$thresh[sp,threshold])] <- "black"  # above threshold
    col[(2:6)[hi>0]] <- NA  # robust negative coef
    col[(2:6)[n<5]] <- NA  # sufficient data points
    
    
    plot(1:5,  rep(0,5),ylim=ylim, xlim = c(0.5, 5.5), type= "n", xaxt = "n", yaxt="n", ann=F)

    axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
    if (i %in% c(10:13)) text(y=-1.6, x = 1:5, labels= abclasses[2:6],  cex=0.9, srt=45, adj=1, xpd = NA)
    
    if ( i %in% c(1,5,9,13)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
    abline(h=0,lty="dotted")
    abline(v = M$thresh[sp,threshold]-1, lty="dashed")
    
    if (!all(is.na(small))) points(1:5, small, pch=".")  
    
    ## Add bootstrapped CI
    if ( !all(is.na(c(hi, low)))) {
      arrows(1:5,low,   1:5,hi, lwd=1, code =3, length=0.05, angle=90)
    }
    
    # draw the points and lines
    par(new=T)
    plot(1:5,es, bg = col[2:6], pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
    
    # Add species name
     mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)
    
    
    # Y axis label
    if ( i %in% c(1,5,9,13)) {  
    mtext(2, text="GLM coefficient",adj=0.5, cex=0.7, line=1.5, las = 0)
    }
   }

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect on alien alpha richness"), adj=0.5, line=4, las = 0, outer=T)

```

### Figure 3: trends in gamma effect size for `r length(impsp)` species:
```{r gammatrendsES, echo=FALSE}

par(mfrow = c(4,4), mar=c(0,0,2,1), oma=c(6,6,2,1))
ylim = c(-50,35)
xlim = c(0.5, 5.5)

for (i in 1 : length(impsp)){
  
  # if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (gamma.trend.nat$P.gamma[sp,] <=0.025) +1]
  n <- as.numeric(glmSRnat.overall$n.obs[sp,])[1:6]
  # create x axis for the 5 abundance classes
  x = c(0:5)

  # create y axis with the gamma richness Standardized effect size
  y = (gamma.trend.nat$obs[sp,] - gamma.trend.nat$mean.null[sp,])
  y [ (1:6)[ n < 5] ]=NA
  y[1]=NA


  # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)

  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(9:12)) text(y=-57, x = 1:5, labels= abclasses[2:6],  cex=1, srt=45, adj=1, xpd = NA)

  axis(2, tcl= 0.1, label=F,  mgp=c(1,0.5,0), las=1)
  if ( i %in% c(1,5,9)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)
  abline(h=0,lty="dotted")
  abline(v =glmSRnat.overall$impact.spread[sp,threshold]-1, lty="dashed")


  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)

  # Add species name
  mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)

  # Y axis label
  if ( i %in%  c(1,5,9)){
    mtext(2, text="ES",adj=0.5, cex=0.8, line=1.5, las = 0)
  }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=4.5, las = 1, outer=T)
mtext(2, text=c("Native gamma richness"), adj=0.5, line=4, las = 0, outer=T)

```



### Figure 4: Graphs of delta gamma vs. different variables:

```{r deltagamma.plots, echo = FALSE}
par(mfrow = c(1,2), mar=c(5,4,2,1), oma=c(0,0,0,0), las = 1)

# loss in gamma vs. loss in alpha
dg<- table.div.part$deltagamma - table.div.part$delta.null.permute.all
dg1<- table.div.part$deltagamma - table.div.part$delta.null.beta

da<- table.div.part$deltaalpha -  table.div.part$deltaalpha.null

cgam <- c("grey50", "black")[ (table.div.part$GRP.permute.all<=0.05) + 1]
plot(da, dg ,pch = 20, col=cgam , ann=F,ylim=c(-60,1), xlim= c(-6,0.5), type ="n")

text(x = da,y = dg,label = rownames(table.div.part) , col=cgam, cex =0.7)
text(x = da,y = dg1,label = rownames(table.div.part) , col="mediumorchid", cex =0.7)

f <- cor.test(da ,dg)
mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

f <- cor.test(da ,dg1)
mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
     line=1,  adj = 1, cex=0.8, col = "mediumorchid")

mtext(1,text = expression(Delta*" alpha richness"), line=3.5 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0)
mtext(3,text = "a)", line=0.5  , las=0, adj = 0, cex =0.85)


## threshold
thresh <-  table.div.part$th.CI

plot (thresh ,dg , pch = 20, col=cgam , ann=F, ylim=c(-60,1),xlim= c(1.5,6.5), type = "n", xaxt ="n")
text(x = thresh , y = dg,label = rownames(table.div.part) ,col="black", cex =0.7 )
text(x = thresh , y = dg1,label = rownames(table.div.part) ,col="mediumorchid", cex =0.7 )

axis(1, tcl = -0.4, label=FALSE)
text(y=-65, x = 2:6, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)

f <- cor.test(thresh ,dg, method = "spearm")
mtext(3, text = substitute(rho == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

f <- cor.test(thresh ,dg1, method = "spearm")
mtext(3, text = substitute(rho == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      line= 1, col = "mediumorchid", adj = 1, cex=0.8)

mtext(1,text = "Critical abundance", line=3.5)
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0)
mtext(3,text = "b)", line=0.5  , las=0, adj = 0, cex =0.85)

```

---

## some alternative figures : 

### SES of deltas 
```{r SES of deltagamma, echo=F }

par(mfrow = c(1,2), mar=c(5,4,2,1), oma=c(0,0,0,0), las = 1)

# loss in gamma vs. loss in alpha
dg<-table.div.part$delta.z.permute.all
dg1<- table.div.part$delta.z.beta
da<-  table.div.part$deltaalpha.z.permute.all

cgam <- c("grey50", "black")[ (table.div.part$GR.P<=0.05) + 1]
plot(da, dg ,pch = 20, col=cgam , ann=F,ylim=c(-4,1), xlim= c(-4,0.5), type ="n")

text(x = da,y = dg,label = rownames(table.div.part) , col="black", cex =0.7)

f <- cor.test(da ,dg)
mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = expression("SES of "*Delta*" alpha richness"), line=3.5 )
mtext(2,text = expression("SES of "*Delta*" gamma richness"), line=2.5  , las=0)
mtext(3,text = "a)", line=0.5  , las=0, adj = 0, cex =0.85)


## threshold
thresh <-  table.div.part$th.CI
f <- cor.test(thresh ,dg, method = "spearm")

plot (thresh ,dg , pch = 20, col=cgam , ann=F, ylim=c(-4,1),xlim= c(1.5,6.5), type = "n", xaxt ="n")
text(x = thresh , y = dg,label = rownames(table.div.part) ,col="black", cex =0.7 )
axis(1, tcl = -0.4, label=FALSE)
text(y=-65, x = 2:6, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Critical abundance", line=3.5)
mtext(2,text = expression("SES of "*Delta*" gamma richness"), line=2.5  , las=0)
mtext(3,text = "b)", line=0.5  , las=0, adj = 0, cex =0.85)
```

### Loss in alpha richness vs. critical abundance
Mean loss in alpha richness is not correlated to the critical abundance value, although 

```{r deltaalpha.vs.crit, echo =FALSE}
da<-  table.div.part$deltaalpha


thr <-  glmSRnat.overall$impact.spread[impsp,  "th.CI"]

plot (thr,da, pch = 20, col=cgam , ann=F,  type="n")
f <- cor.test(da,thr)

text(x = thr,
     y = da, label = impsp ,col="black", cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "critical abundance", line=2.5, cex =0.85 )
mtext(2,text ="alpha loss", line=2.5  , las=0, cex =0.85)

print(f)
```


### Trends in gamma above vs.below trends
```{r gamma.above-below, echo = FALSE}
par(mfrow = c(4,4), mar=c(0,0,1,1), oma=c(6,6,2,1))

list.data <-gamma.above.nat
gamma.loss <- as.data.frame(matrix(NA, nrow = length(impsp), ncol =6))
rownames(gamma.loss) <- impsp

ylim=c(-1,1)
for (i in 1 : length(impsp)){
  
  # if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (list.data$P.above[sp,] <=0.025) +1]
  n <- list.data$nplot.above[sp,]
  # create x axis for the 5 abundance classes
  x = c(0:5)
  
  # create y axis with the gamma richness Standardized effect size
  y =  (list.data$gamma.above[sp,] - list.data$null.above[sp,])/ list.data$null.above[sp,]
  y [ (1:6)[ n < 5 | is.na(n)] ]=NA
  y[1]=NA
  
  gamma.loss[sp,] = y
  
  # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)
  
  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(10:13)) text(y=-1.2, x = 1:5, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
  
  if ( i %in% c(1,5,9,13)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
  abline(h=0,lty="dotted")
  
  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
  
  # Add species name
  mtext(3, text=paste(species[sp, "Genus"], "\n",species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=-2.5, las = 1)
  
  #   # Y axis label
  #   if ( i %in% c(1,4,7)) {  
  #     mtext(2, text="SES", ,adj=0.5, cex=0.8, line=1.5, las = 0)
  #   }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect size of native gamma richness"), adj=0.5, line=3, las = 0, outer=T)
```


### Loss in gamma richness vs. spatial proportion of potential impact

```{r deltagam.impactproportion, echo =FALSE}
par(mfrow = c(1,1), mar=c(4,4,2,1), oma = c(1,1,1,1))
spread <-  glmSRnat.overall$impact.spread[impsp,  "prop.plot.impact"]
plot (spread,dg , pch = 20, col=cgam , ann=F, xlim =c(0, 1), type="n")
f <- cor.test(spread ,dg)

text(x = spread,
     y = dg,
     label = rownames(table.div.part) ,col="black", cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "Prop. of plots > critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
```


### Change in gamma frequency above/below critical threshold on native richness 
```{r}
# par(mfrow=c(4,4), mar=c(2,2,2,2), oma= c(2,3,1,1))
# for (sp in impsp) {
# 
#   community <- comm[which((rownames(comm) %in% realgrasslands) & (comm[,sp]>0) ),-grep(sp, names(comm))]
#   community <- ceiling(community>0)
#   community <- community[,colSums(community)>0]
# 
#   comm.nat<- community[,colnames(community) %in% natives]
#   comm.ali<- community[,colnames(community) %in% aliens]
# 
#   var <- comm[rownames(community),sp]
#   var[var < glmSRnat.overall$impact.spread [sp,"th.CI"]] <- 0
#   var[var >= glmSRnat.overall$impact.spread [sp,"th.CI"]] <- 1
# 
#   B.freq <- colSums(comm.nat[var==0,])/sum(var==0)
#   A.freq <- colSums(comm.nat[var==1,])/sum(var==1)
#   B.freq.ali <- colSums(comm.ali[var==0,])/sum(var==0)
#   A.freq.ali <- colSums(comm.ali[var==1,])/sum(var==1)
# 
#   cvec <-  c("black","red")[(A.freq == 0) + 1]
#   sum((A.freq == 0) )
#   cvec [B.freq == 0] <- "forestgreen"
#   sum(B.freq == 0)
# 
#   f1 <- wilcox.test(  A.freq ,B.freq, paired=T, alternative = "less")
#   c1 <- cor.test( A.freq , B.freq, method = "spearman")
# 
#   #correlation plot
# #   plot(jitter(B.freq, factor = 1), jitter(A.freq, factor=1),
# #        ylim=c(-0.01,0.9), xlim=c(-0.01,0.9),pch=21, bg =cvec,
# #        ann=F, axes =F)
#   plot(B.freq+0.005, A.freq+0.005,log="xy",type = "n", pch=21, bg =cvec, ann=F, axes =F,
#        ylim=c(0.005, 0.9), xlim=c(0.005,0.9))
# 
#   abline(0,1)
#   mtext(paste(sp, "\n rho=", round(c1$est, 2), p2star(c1$p.val)), cex = 0.7)
# 
#   points(B.freq.ali+0.005, A.freq.ali+0.005,log="xy",pch=3, cex=0.85, col="grey")
#   points(B.freq+0.005, A.freq+0.005, pch=21, bg =cvec)
# 
# #   axis(1, at =c(0.005,0.01,seq(0.1,0.9,0.1)),label=c(0,0.01,seq(10,90,10)), tcl = 0.2,mgp=c(1,0.2,0), cex=0.7)
# #   axis(2, at =c(0.005,0.01,seq(0.1,0.9,0.1)),label=c(0,0.01,seq(10,90,10)), tcl = 0.2,mgp=c(1,0.2,0),las=1,  cex=0.7)
#   axis(1, tcl = 0.2,mgp=c(1,0.2,0), cex=0.7)
#  axis(2,tcl = 0.2,mgp=c(1,0.2,0),las=1,  cex=0.7)
# 
#   box(bty="l")
# }
# mtext(side = 1, text =c("below critical"),cex = 1, line=0,outer= T)
# mtext(side = 2, text =c("above critical"),cex = 1, line= 1,outer= T)
```


