---
title: "Impact thresholds article"
author: "maudbv"
date: "6 August 2015"
output: html_document
---

```{r setup, include=FALSE, echo =T}
knitr::opts_chunk$set(echo = TRUE,
                      root.dir = "C:/Users/bernarm2/Dropbox/Work/doc boulot/post doc Lincoln/R_alienimpactBP")
knitr::opts_chunk$get()

```

```{r loaddata}
setwd("C:/Users/bernarm2/Dropbox/Work/doc boulot/post doc Lincoln/R_alienimpactBP")
## load data and results
load("saved Rdata/article 2 - threshold/article threshold 1.2.Rdata")

#default grpahical parameters
.defaultpar <- par(no.readonly = T)

```

## Results and figures for the article on low-abundance impacts of alien plants

Title
=====
## Tables and numbers
## Including Plots

# Figures  for the article
```{r define.param}
abclasses= c("Rare" ,"Occasional",  "Frequent", "Common", "Abundant","Dominant")
threshold ="th.CI"
sel <- impsp

```

# Figure 1: barplot of frequencies 
```{r frequency, echo=FALSE}

effects =list(glmSRnat.sum$class.summary,glmSRali.sum$class.summary )     

n <- length(unique(effects[[1]]$group)) 

par(mfcol=c(n,2), oma=c(5,6,4,1), mar=c(1,1,1,2), las=1)
for (j in 1:2) {
  sum.df = effects[[j]] 
  for (i in 1:n) {
    S <- as.data.frame(sum.df[sum.df$group == unique(sum.df$group)[i],])
    S$prop.negative.target <- S$n.negative.target/S$n.target
    
    barplot(S$nb.sp, ylim=c(0,max(40, S$nb.sp)),
            col= "grey",  border= NA, axes=F)
    par(new=T)
    b <- barplot(S$freq.thr, col="black" , ylim=c(0,max(40, S$nb.sp)), border= NA, axes=F)
    axis(2, tcl = -0.3, cex.axis = 0.8, mgp = c(1,0.5,0))
    if (i==2) text(y=-3, x = b, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
    
    if (j==2 & i==1) {
      legend(x=0.3, y=40, bty="n", bg="white",legend=c("Critical abundance", "Total occurrences"),
             fill=c("black",  "grey"), border= c("black",  "grey"), cex=0.9, xpd=NA)
    }
    if(j==1) {
      mtext(text="number of species", side=2, outer=F, line=1.5, las=0, cex=0.85) 
    }
  }   
}

mtext(side=2, text=c("Alien\nfocal\nspecies", "Native\nfocal\nspecies"),line=4, at=c(0.25,0.75),adj=0.5, outer=T, las=1)
mtext(side=3, text=c("a) Native richness", "b) Alien richness"),line=0, at=c(0.25,0.75),adj=0.5, outer=T, las=1)

mtext(text="Abundance class", side=1, outer=T, line=3)
```
  
# Figure 2: trends in alpha effect size for 11 species
```{r alphatrends, echo = FALSE}

par(mfrow = c(3,4), mar=c(0,0,2,2), oma=c(6,6,2,3))

M <- glmSRnat.overall
  ylim=c(-3,3)
  ### Loop on selected species 
  for (i in 1:length(sel))  {
    if (i ==4) plot.new()
    sp <- sel[i]
    es <- as.numeric(M$est[sp,])
    n <- as.numeric(M$n.obs[sp,])[2:6]
    
      low <- as.numeric(M$CIlow[sp,])
      hi <- as.numeric(M$CIhi[sp,])
      M$thresh <-M$impact.spread
    
    ## correct for small sample sizes
    small <- es
    small[which(n>=3)] <- NA
    es[which(n<3)] <- NA
    low[n<3] <- NA
    hi[n<3] <- NA
    
    if ( !all(is.na(c(hi, low)))) lims <-  max(c(abs(low),abs(hi)), na.rm=T) +0.02
    if ( all(is.na(c(hi, low)))) lims <-  max(c(abs(es)), na.rm=T) +0.02

    col <- rep("white",6)
    col[(1:6)>= as.numeric( M$thresh[sp,threshold])] <- "black"  # above threshold
    col[(2:6)[hi>0]] <- NA  # robust negative coef
    col[(2:6)[n<5]] <- NA  # sufficient data points
    
    
    plot(1:5,  rep(0,5),ylim=ylim, xlim = c(0.5, 5.5), type= "n", xaxt = "n", yaxt="n", ann=F)

    axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
    if (i %in% c(8:11)) text(y=-3.6, x = 1:5, labels= abclasses[2:6],  cex=0.9, srt=45, adj=1, xpd = NA)
    
    if ( i %in% c(1,4,8)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
    abline(h=0,lty="dotted")
    abline(v = M$thresh[sp,threshold]-1, lty="dashed")
    
    if (!all(is.na(small))) points(1:5, small, pch=".")  
    
    ## Add bootstrapped CI
    if ( !all(is.na(c(hi, low)))) {
      arrows(1:5,low,   1:5,hi, lwd=1, code =3, length=0.05, angle=90)
    }
    
    # draw the points and lines
    par(new=T)
    plot(1:5,es, bg = col[2:6], pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
    
    # Add species name
     mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
          font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)
    
    
    # Y axis label
    if ( i %in% c(1,4,8)) {  
    mtext(2, text="GLM coefficient",adj=0.5, cex=0.7, line=1.5, las = 0)
    }
   }

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect on native alpha richness"), adj=0.5, line=4, las = 0, outer=T)

```

# Figure 3: trends in gamma effect size for 11 species

```{r gammatrends, echo=FALSE}

par(mfrow = c(3,4), mar=c(0,0,1,1), oma=c(6,6,2,1))
ylim = c(-50,35)
xlim = c(0.5, 5.5)
for (i in 1 : length(impsp)){
  
  if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (gamma.trend.nat$P.gamma[i,] <=0.025) +1]
  n <- as.numeric(M$n.obs[sp,])[2:6]
  # create x axis for the 5 abundance classes
  x = c(0:5)

  # create y axis with the gamma richness Standardized effect size
  y = (gamma.trend.nat$obs[i,] - gamma.trend.nat$mean[i,])
  y [ (2:6)[ n < 5] ]=NA
  y[1]=NA


  # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)

  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(8,9,10,11)) text(y=-50.2, x = 1:5, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)

  if ( i %in% c(1,4,8)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)
  abline(h=0,lty="dotted")

  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)

  # Add species name
  mtext(3, text=paste(species[sp, "Genus"]," ", species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=0.2, las = 1)

#   # Y axis label
#   if ( i %in% c(1,4,7)) {
#     mtext(2, text="SES", ,adj=0.5, cex=0.8, line=1.5, las = 0)
#   }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect size of native gamma richness"), adj=0.5, line=3, las = 0, outer=T)

```

# Figure 4: Graphs of delta gamma vs. different variables

```{r deltagamma.plots, echo = FALSE}

## colors for gamma loss significance
cgam <- c("grey50", "black")[ (divpart.nat.perm$P$above.gamm<=0.05 | divpart.nat.perm$P$above.gamm>=0.95) + 1]

### figure 4 panels : ##########
dg<- -(table.div.part$GRc - table.div.part$GRnull )
# dg<- -(table.div.part$GRc - table.div.part$GRnull )/table.div.part$GRsdnull
da<-  -( table.div.part $aRc -table.div.part$aRo )
cgam <- c("grey50", "black")[ (table.div.part$GR.P<=0.05) + 1]

par(mfrow = c(2,2), mar=c(4,4,2,2), las = 1)
plot(da, dg ,pch = 20, col=cgam , ann=F,ylim=c(1,40), xlim= c(1,10), type ="n")

text(x = da,y = dg,label = rownames(divpart.nat.perm$P) , col=cgam, cex =0.85)

f <- cor.test(da ,dg)
mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = expression(Delta*" alpha richness"), line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
mtext(3,text = "a)", line=0.5  , las=0, adj = 0, cex =0.85)


## threshold
thresh <-  glmSRnat.overall$impact.spread[impsp,  "th.CI"]
plot (thresh ,dg , pch = 20, col=cgam , ann=F, xlim= c(1,6.5), type = "n")
f <- cor.test(thresh ,dg)

text(x = thresh , y = dg,
     label = rownames(divpart.nat.perm$P) ,col=cgam, cex =0.85 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
mtext(3,text = "b)", line=0.5  , las=0, adj = 0, cex =0.85)

### gamma above/below against threhold values
spread <-  glmSRnat.overall$impact.spread[impsp,  "n.plot.impact"]
plot (spread,dg , pch = 20, col=cgam , ann=F, log = "x", xlim =c(2.5, 700), type= "n")
f <- cor.test(spread ,dg)
text(x = spread,
     y = dg,
     label = rownames(divpart.nat.perm$P) ,col=cgam, cex =0.85)

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Number of plots > critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
mtext(3,text = "c)", line=0.5  , las=0, adj = 0, cex =0.85)

# spatial clustering
cluster<-  mnnd.th[impsp, "P<obs_above"]
cluster<- - (mnnd.th[impsp, "mnnd.obs_above"] - mnnd.th[impsp, "null.mean_above"])/ mnnd.th[impsp, "null.sd_above"] 
plot (cluster,dg , pch = 20, col=cgam , ann=F,  type="n",xlim=c(-1,2.6))
f <- cor.test(cluster ,dg)

text(x = cluster,
     y = dg,
     label = rownames(divpart.nat.perm$P) ,col=cgam, cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 1, cex=0.8)

mtext(1,text = "Spatial clustering of plots > critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
mtext(3,text = "d)", line=0.5  , las=0, adj = 0, cex =0.85)

```


# alternative figures : 

# gamma above vs.below trends
```{r gamma.above-below, echo = FALSE}
par(mfrow = c(3,4), mar=c(0,0,1,1), oma=c(6,6,2,1))

list.data <-divpart.nat.perm
gamma.loss <- as.data.frame(matrix(NA, nrow = length(impsp), ncol =6))
rownames(gamma.loss) <- impsp

ylim=c(-1,1)
for (i in 1 : length(impsp)){
  
  if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (list.data$P.above[i,] <=0.025) +1]
  n <- as.numeric(M$n.obs[sp,])[2:6]
  # create x axis for the 5 abundance classes
  x = c(0:5)
  
  # create y axis with the gamma richness Standardized effect size
  y =  (list.data$gamma.above[i,] - list.data$null.above[i,])/ list.data$null.above[i,]
  y [ (2:6)[ n < 5] ]=NA
  y[1]=NA
  
  gamma.loss[sp,] = y
  
  # plot background
  plot(x,y,ylim=ylim, xlim = c(0.5, 5.5), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)
  
  axis(1,at = 1:5, label = rep("",5), tcl= 0.1,mgp=c(1,0.5,0),las=1)
  if (i %in% c(8,9,10,11)) text(y=-1.2, x = 1:5, labels= abclasses[2:6],  cex=0.8, srt=45, adj=1, xpd = NA)
  
  if ( i %in% c(1,4,8)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
  abline(h=0,lty="dotted")
  
  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(0.5, 5.5), xaxt = "n", yaxt="n", ann=F)
  
  # Add species name
  mtext(3, text=paste(species[sp, "Genus"], "\n",species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=-2.5, las = 1)
  
  #   # Y axis label
  #   if ( i %in% c(1,4,7)) {  
  #     mtext(2, text="SES", ,adj=0.5, cex=0.8, line=1.5, las = 0)
  #   }
}

mtext(1, text=c("Abundance class"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect size of native gamma richness"), adj=0.5, line=3, las = 0, outer=T)
```


# prop of impact
```{r deltagam.impactproportion, echo =FALSE}
spread <-  glmSRnat.overall$impact.spread[impsp,  "prop.plot.impact"]
plot (spread,dg , pch = 20, col=cgam , ann=F, xlim =c(0, 1), type="n")
f <- cor.test(spread ,dg)

text(x = spread,
     y = dg,
     label = rownames(divpart.nat.perm$P) ,col=cgam, cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "Prop. of plots > critical abundance", line=2.5, cex =0.85 )
mtext(2,text = expression(Delta*" gamma richness"), line=2.5  , las=0, cex =0.85)
```


# clustering vs threshold
```{r spatialcluster.vs.crit, echo =FALSE}
cluster<-  (mnnd.th[impsp, "mnnd.obs_above"] - mnnd.th[impsp, "null.mean_above"])/ mnnd.th[impsp, "null.sd_above"] 
thresh <-  glmSRnat.overall$impact.spread[impsp,  "th.CI"]

plot (thresh,cluster, pch = 20, col=cgam , ann=F,  type="n")
f <- cor.test(cluster ,thresh, method = "spearman")

text(x = thresh,
     y = cluster,
     label = rownames(divpart.nat.perm$P) ,col=cgam, cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "critical abundance", line=2.5, cex =0.85 )
mtext(2,text ="SES of MNND", line=2.5  , las=0, cex =0.85)
```

# alpha loss vs threshold
```{r deltaalpha.vs.crit, echo =FALSE}
da<-  -( table.div.part $aRc - table.div.part$aRo )
da<-  as.numeric(impact.SRnat[impsp,]$wtd.mean.dif)
da<-  as.numeric(impact.SRnat[impsp,]$th.dif)

thresh <-  glmSRnat.overall$impact.spread[impsp,  "th.CI"]

plot (thresh,da, pch = 20, col=cgam , ann=F,  type="n")
f <- cor.test(da,thresh, method = "spearman")

text(x = thresh,
     y = da,
     label = impsp ,col="black", cex =0.7 )

mtext(3, text = substitute(r == est *" "*p, list(est = round(f$est,2), p=p2star(f$p.val, marginal=T))),
      adj = 0, cex=0.8)

mtext(1,text = "critical abundance", line=2.5, cex =0.85 )
mtext(2,text ="alpha loss", line=2.5  , las=0, cex =0.85)
```

# spatial clustering vs loss in gamma richness at each abundance  ############
```{r spatialcluster.vs.deltagammaperab, echo = FALSE}
par(mfrow = c(3,4), mar=c(0,0,1,1), oma=c(6,6,2,1))

list.data <-divpart.nat.perm
gamma.loss <- as.data.frame(matrix(NA, nrow = length(impsp), ncol =6))
rownames(gamma.loss) <- impsp

ylim=c(-50,20)
for (i in 1 : length(impsp)){
  
  if (i ==4) plot.new()
  sp <- impsp[i]
  # identify significant classes in black
  cols <- c(NA, "black") [ (list.data$P.above[i,] <=0.025) +1]
  cols [2] <- "red"
  n <- as.numeric(M$n.obs[sp,])[2:6]
  # create x axis for the 5 abundance classes

  # create y axis with the gamma richness Standardized effect size
  
  x= mnnd.above$z[i,]
  
  y =  (list.data$gamma.above[i,] - list.data$null.above[i,])
  y [ (2:6)[ n < 5] ]=NA
  y[1]=NA
  
  gamma.loss[sp,] = y
  
  # plot background
  plot(x,y,ylim=ylim, xlim = c(-5,2), las = 1,type= "p", xaxt = "n", yaxt="n", ann=F,
       pch = 21, col ="black",bg = cols)
  
  axis(1, tcl= 0.1,mgp=c(1,0.5,0),las=1)
    
  if ( i %in% c(1,4,8)) axis(2, tcl= 0.1,  mgp=c(1,0.5,0), las=1)  
  abline(h=0,lty="dotted")
  abline(v=0,lty="dotted")
  
  #plot points and lines
  par(new=T)
  plot(x,y, bg = cols, pch=21, type = "b",ylim=ylim, xlim = c(-5,2), xaxt = "n", yaxt="n", ann=F)
  
  # Add species name
  mtext(3, text=paste(species[sp, "Genus"], "\n",species[sp, "Species"], sep="") ,
        font = 3, outer= F,adj=0.9, cex=0.7, line=-2.5, las = 1)
  
  #   # Y axis label
  #   if ( i %in% c(1,4,7)) {  
  #     mtext(2, text="SES", ,adj=0.5, cex=0.8, line=1.5, las = 0)
  #   }
}

mtext(1, text=c("SES MNND"), adj=0.5, line=4, las = 1, outer=T)
mtext(2, text=c("Effect size of native gamma richness"), adj=0.5, line=3, las = 0, outer=T)
```
